Local simple connectedness of boundaries of hyperbolic groups

### 2020-03-05 paper.tex
Proof reading section 2.3

\begin{definition}
  Let $U_i \subset \boundary G$ be the set of all points in $\boundary G -
  \set\xi$ such that all geodesic rays from $g_i \in G$ to points in $U_i$ pass
  through $H_i$. Let $q_i$ be the restriction of the map $g_i \composed
  p^\infty_{n_i} \composed g_i^{-1}$ to $U_i$.
\end{definition}

The following lemma is immediate from the definition of $p^\infty_i$.

\begin{lemma}\label{lem:describing_q_i}
  The set $q_i(U_i)$ is contained in $H_i$.
  Furthermore, let $\zeta \in U_i$ so that $q_i(\zeta) \in H_i$.  Then
  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
  \begin{equation*}
    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \intersection H_i
  \end{equation*}
  In particular, if $\eta$ is any geodesic ray with $\eta(0) = g_i$ and
  $\eta(\infty) = \zeta$ then $q_i(\zeta)$ is contained in the minimal simplex
  of $H_i$ with vertex set
  \begin{equation*}
    N_{4\delta + 1}(\eta(n_i)) \intersection H_i.
  \end{equation*}
\end{lemma}

@@

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so for each $i$
  there is a geodesic ray $\alpha_i$ from $g_i$ to $\zeta_i$ that does not pass
  through $H_i$. After passing to a subsequence, the rays $\alpha_i$ converge uniformly on compact susbets to a bi-infinite geodesic from $\xi$ to some $\zeta \in C$ that does not meet $H$, contardicting Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

\begin{lemma}\label{lem:affinehomotopic}
  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
  q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
  and $q_{i_0}\restricted{C}$ are related by an affine homotopy.
\end{lemma}

>>>>

\begin{definition}
  For each $i$, let $U_i \subset \boundary G$ be the set $\left(g_i \composed
  p^\infty_{n_i} \composed g_i^{-1}\right)^{-1} H_i$ and let $q_i \from U_i \to
  H_i$ be the restriction of $g_i \composed p^\infty_{n_i}\composed g_i^{-1}$
  to this set.
\end{definition}

The maps $q_i$ are described by the following lemma, which is immediate from
the definition of $p^\infty_i$.

\begin{lemma}\label{lem:describing_q_i}
  \todo{Check this version is strong enough.}
  Let $\zeta \in \boundary G$ be a point such that
  \begin{equation*}
    N_{2\delta+1}^{g_i\cdot S_{n_i}} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
        $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \subset H_i,
  \end{equation*}
  where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a $2\delta+1$-neighbourhood
  in $g_i\cdot S_{n_i}$ taken with respect to the metrid $\dist$.
  Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in the simplex of $H_i$
  spanned by this set of vertices.
\end{lemma}

@@

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
  $\alpha_i$ converge uniformly on compact subsets toa bi-infinite geodesic
  from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

\begin{lemma}\label{lem:affinehomotopic}
  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
  q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
  and $q_{i_0}\restricted{C}$ are related by an homotopy.
\end{lemma}
